Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-01 paper/paper.qmd
Add references in Appendix B and update Reference bib

## Objective and Overview
The goal of this survey methodology is to accurately forecast the outcome of the U.S. presidential election by collecting high-quality, representative data from a diverse set of respondents across the country. With a budget of \$100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols. The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.

## Core Objectives
* Obtain a representative sample of the U.S. electorate.
* Ensure data quality through rigorous validation.
* Leverage statistical modeling and poll aggregation for an accurate prediction.

## Sampling Strategy
The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population. To achieve this, we will use **stratified random sampling** combined with **quota sampling** for key demographics. This ensures that each important subgroup within the population is adequately represented.

@@

@@

## Recruitment Strategy
To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:

@@

## Poll Aggregation and Data Analysis
### Poll Aggregation
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach.

@@

## Survey Implementation
The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection. You can access the survey at the following link: [Google Form Survey](https://forms.gle/XxtMTMc45d6VzNuy8)

>>>>

## Objective and Overview
The primary goal of this survey methodology is to forecast the outcome of the U.S. presidential election by collecting high-quality, representative data from a diverse cross-section of American voters. Given a budget of $100,000, this methodology leverages sophisticated sampling techniques, effective respondent recruitment strategies, and robust data validation protocols to ensure maximum accuracy and minimal bias. This approach is designed to account for demographic, geographic, and political factors that can influence voting behavior, thereby enhancing the reliability of predictions [@fivethirty; @pewresearch].

## Core Objectives
* Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
* Ensure data quality through rigorous validation processes, including screening and cross-verification.
* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling [@silver_nytimes].

## Sampling Strategy
Our sampling strategy combines **stratified random sampling** with **quota sampling** to ensure broad representation across key demographics. This method has been shown to improve the accuracy of electoral predictions by reducing demographic and geographic sampling bias [@fivethirty].

@@

This stratification aligns with best practices in survey sampling, allowing for improved accuracy and generalizability in election forecasting [@pewresearch].

@@

## Recruitment Strategy
Recruitment is executed through  **multi-channel outreach**, combining digital advertisements, email outreach, and partnerships with civic organizations. This diverse recruitment strategy helps to capture a representative sample and has been identified as a best practice in survey methodologies [@pewresearch].

@@

These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @silver_nytimes].

## Poll Aggregation and Data Analysis
### Poll Aggregation
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@silver_nytimes].

@@

## Survey Implementation
The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection. You can access the survey at the following link: [Google Form Survey](https://forms.gle/sAxVuk3n9gV8e2odA)
